Thermodynamic response functions in a cell fluid model

### 2024-09-10 dobush_et_al_ujp_UTF8.tex

\begin{document}
	\title[Колонтитул: Назва роботи (3-5 слів)/Headline: paper title (3-5 words)]%колонтитул
	{НАЗВА РОБОТИ/PAPER TITLE}%
	\author{Прізвище автора 1/Name of Author 1}%1
	\affiliation{Bogolyubov Institute for Theoretical Physics, Nat. Acad. of Sci. of Ukraine}%інститут 1
	\address{14b, Metrolohichna Str., Kyiv 03143, Ukraine}%адреса 1
	\email{ujp@bitp.kiev.ua}%e-mail 1
	\author{Прізвище автора 2/Name of Author 2}%2
	\affiliation{Department of Mathematics and Computer science, Universiteit Antwerpen}%інститут 2
	\address{Middelheimlaan 1, Antwerpen 2020, Belgium}%адреса 2

	\udk{№ УДК/UDC} \razd{\secix}

	\autorcol{N.N.\hspace*{0.7mm}Author1, N.N.\hspace*{0.7mm}Author2, N.N.\hspace*{0.7mm}Author3 et al.}%

@@

	\begin{abstract}
		Аннотація/Abstract
	\end{abstract}

	\keywords{Ключові слова/Keywords.}

@@

	\section{Вступ/Introduction}

	Текст роботи/Paper text...

	\section{Розділ/Section}

	Для всіх формул вирівнювання ліворуч./All formulas should be shifted to the left.

	Для формул з номером:/For numbered formulas:
	\begin{equation}
	\end{equation}
	Для формул без номерів:/For unnumbered formulas:
	\[
	\]

	Для рисунків:/For figures:%

	%Fig.~1
	\begin{figure}% figure* for wide figure, [h] [!] to change the placement
		\vskip1mm
		%\includegraphics[width=\column]{1_e}
		\vskip-3mm\caption{  }
	\end{figure}

	Для таблиць:/For tables:% Таблиця 5х4

	\begin{table}[b]
		\noindent\caption{Назва таблиці/Table title}\vskip3mm\tabcolsep4.5pt

		\noindent{\footnotesize
			\begin{tabular}{|c|c|c|c|c}
				\hline%
				\multicolumn{1}{|c}{\rule{0pt}{5mm}Назва 1-ї колонки/Title of 1st column}%
				& \multicolumn{1}{|c}{Назва 2-ї колонки/Title of 2nd column}
				& \multicolumn{1}{|c}{Назва 3-ї колонки/Title of 3d column}
				& \multicolumn{1}{|c}{Назва 4-ї колонки/Title of 4th column}
				& \multicolumn{1}{|c|}{Назва 5-ї колонки/Title of 5th column}\\[2mm]%
				\hline%
				\rule{0pt}{5mm}&&&&\\ % Приклад/Example: 1&2&3&4&5\\
				&&&&\\%
				&&&&\\[2mm]%
				\hline
			\end{tabular}
		}
	\end{table}

	\section{Висновки/Conclusions}

	\vskip3mm \textit{Подяка/Acknowledgement.}

	\begin{thebibliography}{99}

		\bibitem{RoSmo} C.~Rovelli, L.~Smolin. Spin networks and quantum
		gravity. \textit{Phys. Phys. D}  {\bf 52}, 5743 (1995). [DOI: https://doi.org].%1

		\bibitem{Sho90} B.W.~Shore. \textit{The Theory of Coherent Atomic Excitation}
		(Wiley,  1990) [ISBN: 978-0471524175].%2

		\bibitem{3}
		\bibitem{4}

		\begin{flushright}
			{\footnotesize Received 26.01.18}
		\end{flushright}
	\end{thebibliography}

	Якщо стаття англ. мовою/For papers in English:

	\vspace*{-5mm}\rezume{%Резюме укр. мовою
		А.А. Автор1, А.А. Автор2, А.А. Автор3 та ін.}{НАЗВА СТАТТІ УКР.
		МОВОЮ} {Текст резюме укр. мовою.}{\textit{К\,л\,ю\,ч\,о\,в\,і\,
			с\,л\,о\,в\,а:} ключові слова.}

	Якщо стаття укр. мовою/For papers in Ukrainian:

	\rezumang{%Резюме англ. мовою
		N.N. Author1, N.N. Author2, N.N. Author3 et al.}{PAPER TITLE IN
		ENGLISH}{Annotation text.}{\textit{Keywords:} keywords.}

>>>>

\usepackage{orcidlink} % to insert a hyperlinked ORCiD logo
\usepackage{amssymb}
\usepackage{physics}
%\usepackage{cite} % may be useful for different formats of numerical citation
\usepackage{hyperref} % for hyperlinks in references
\usepackage[nameinlink]{cleveref}
\usepackage{caption} % for \caption*
\usepackage{amsmath}    % for "\eqref" macro
\usepackage{graphicx}

\begin{document}
	\title[Thermodynamic response functions in a cell fluid model]%колонтитул
	{THERMODYNAMIC RESPONSE FUNCTIONS IN A CELL FLUID MODEL}%
	\author{O.A.~Dobush}%1
	\author{M.P.~Kozlovskii}
	\author{R.V.~Romanik}
	\author{I.V.~Pylyuk}
	\affiliation{Institute for Condensed Matter Physics,\\ Nat. Acad. of Sci. of Ukraine}%інститут 1
	\address{1, Svientsitskii Str., Lviv 79011, Ukraine}%адреса 1
	\email{dobush@icmp.lviv.ua}%e-mail 1
	\email{mpk@icmp.lviv.ua}
	\email{romanik@icmp.lviv.ua}
	\email{piv@icmp.lviv.ua}

	\udk{№ УДК/UDC} \razd{\secv}

	\autorcol{O.A.\hspace*{0.7mm}Dobush, M.P.\hspace*{0.7mm}Kozlovskii, R.V.\hspace*{0.7mm}Romanik, I.V.\hspace*{0.7mm}Pylyuk}%

@@

	\begin{abstract}
		Thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, are calculated for a many-particle system interacting through a modified Morse potential. These calculations are based on an equation of state previously derived for a cell fluid model in the grand canonical ensemble. The calculated quantities are presented graphically as functions of density and chemical potential.
	\end{abstract}

	\keywords{Cell model, Morse potential, Thermodynamic response functions}

@@

	\input{./paper_text.tex}

	\vskip3mm \textit{Acknowledgement.}

	\bibliography{extracted}

	\vspace*{-5mm}\rezume{%Резюме укр. мовою
		О.А.~Добуш, М.П.~Козловський, Р.В.~Романік, І.В.~Пилюк}{ТЕРМОДИНАМІЧНІ ФУНКЦІЇ ВІДГУКУ КОМІРКОВОЇ МОДЕЛІ} {Текст резюме укр. мовою.}{\textit{К\,л\,ю\,ч\,о\,в\,і\,
			с\,л\,о\,в\,а:} коміркова модель, потенціал Морзе, термодинамічні функції відгуку.}
